Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-11 Papers/ms.tex
Comment about another level of hierarchy
More words about the posterior for mu_lens

If we are interested in detecting and measuring the properties of
possible dark substructures in a lens galaxy,
a superposition of an unknown number of ``blobs'' is the
most natural model. In addition, if we want to constrain the mass function of
these blobs \citep[e.g.][]{2009MNRAS.400.1583V, 2014MNRAS.442.2017V},
we will need a hierarchical model which specifies the prior probability
distribution for the masses conditional on some hyperparameters. Inferring the
mass function of the blobs then reduces to calculating the posterior
distribution for the hyperparameters. This is related to the general principle
that we should (ideally) construct our inference methods so that the
quantities we infer directly answer our scientific questions
\citep{2015arXiv150507840A, 2015ApJ...807...87S, pancoast}.

@@

{\revisions
To demonstrate the claim that we can infer something about the mass function
of substructures directly, we have plotted the posterior
distribution for $\mu_{\rm lens}$, the hyperparameter for the substructure
masses, in Figure~\ref{fig:mu_lens}.
}

>>>>

If we are interested in detecting and measuring the properties of
possible dark substructures in a lens galaxy,
a superposition of an unknown number of ``blobs'' is the
most natural model. In addition, if we want to constrain the mass function of
these blobs \citep[e.g.][]{2009MNRAS.400.1583V, 2014MNRAS.442.2017V},
we will need a hierarchical model which specifies the prior probability
distribution for the masses conditional on some hyperparameters. Inferring the
mass function of the blobs then reduces to calculating the posterior
distribution for the hyperparameters. This is related to the general principle
that we should (ideally) construct our inference methods so that the
quantities we infer directly answer our scientific questions
\citep{2015arXiv150507840A, 2015ApJ...807...87S, pancoast}.
{\revisions Here, we are referring to
the mass function of the substructures within a single lens galaxy. An
additional level of hierarchy would be needed to answer questions about a
sample of lens galaxies}.

@@

{\revisions
To demonstrate the claim that we can infer something about the mass function
of substructures directly from the image data, we have plotted the posterior
distribution for $\mu_{\rm lens}$, the hyperparameter for the substructure
masses, in Figure~\ref{fig:mu_lens}. The true value was 1, and the
posterior distribution indicates a fairly wide uncertainty range that is
at least consistent with the true value in some sense. Given that the image
only contained a few substructures whose masses could be measured with any
accuracy, the large uncertainty is not surprising.
}
